### 2017-05-04 manuscript.rmd
added significance statement

---
bibliography: manuscript.bib
csl: nature.csl
output:
  pdf_document:
    fig_caption: yes
    fig_width: 6
    fig_height: 4

@@

>>>>

---
bibliography: manuscript.bib
csl: pnas.csl
output:
  pdf_document:
    fig_caption: yes
    fig_width: 6
    fig_height: 4

@@

## Significance

Comparisons of genome function between species are providing important insight into the evolutionary origins of diversity. Here we demonstrate that comparative functional genomics studies can come to the wrong conclusions if they do not take the relationships of species into account and instead rely on pairwise comparisons between species, as is common practice. We re-examined two previously published studies and found problems with pairwise comparisons that draw both their original conclusions into question. One study had found support for the ortholog conjecture and the other had concluded that the evolution of gene expression was different between animal phyla than within them. Our results demonstrate that to answer evolutionary questions about genome function, it is critical to consider evolutionary relationships.
